BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-02 tex/5-evaluation.tex
Eval++ before mergin vengelis comments

% setup
Our measurements were made with garbage collector disabled on a otherwise idle core of an \TODO{Intel X} processor. Experimental data where obtained by taking the median of 11 mesurements. confidence intervals .. in .. as (max 0.002 sec)

>>>>

% setup
Our measurements were made with garbage collector disabled on a otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor. Experimental data was obtained by taking the median of 11 mesurements. On this setup we obtained very low standard deviations on the order of 2 milliseconds which are therefor

confidence intervals .. in .. as (max 2ms)
